Unified Understanding of the Dielectric Nature of Two-Dimensional Materials

### 2018-10-29 paper.tex
Add paragraph about dielectric anisotropy

Figure \ref{fig-3}a shows the calculated bandgap $E_{\mathrm{g}}$
(blue dots) and polarizabilities (bar plots) of all the 2D materials
investigated, covering a wide spectrum range from far infrared to
ultraviolet. From dimension analysis, it is more intuitive to express
the polarizability as $\alpha/(4 \pi \varepsilon_{0})$, which has unit
of \AA. We find that $\alpha^{\parallel}$ has a general descending
trend when $E_{\mathrm{g}}$ increases. On the other hand, no apparent
trend between $\alpha^{\perp}$ and $E_{\mathrm{g}}$ is observed (see
Supplementary Section S2.2).  Combining recent theoretical findings of
the universal linear relation between exciton binding energy
$E_{\mathrm{b}}$ and bandgap $E_{\mathrm{g}}$ of 2D materials
\cite{Choi_linear_2015,Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}, and the
fact that the $E_{\mathrm{b}}$ is roughly inversely proportional to
$\alpha^{\parallel}$ \cite{Pulci_2014}, it is reasonable to guess that
a general Moss-like relation between $E_{\mathrm{g}}$ and
$1/\alpha^{\parallel}$ may exist for 2D materials. On the other hand,
the bandgap-independent relation of $\alpha^{\perp}$ resembles
molecular polarizabilities of conjugate molecules \cite{Davies_1952},
fullerenes \cite{Sabirov_2014} and carbon nanotubes
\cite{Benedict_1995}, which are shown to be geometry-dependent. Next
we show that the universal Moss-like relations exist for both
$\alpha^{\parallel}$ and $\alpha^{\perp}$.

We now validate Eq. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp}
using the polarizabilities calculated by first principle
calculations. Figure \ref{fig-3}b shows
$(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ (in \AA{}) as a function
of $E_{\mathrm{g}}$ (in eV) for the 2D materials investiaged (circle
dots), with a linear regression slope of ~0.182 and $R^{2}$ of
0.84. From Ref. \citenum{Jiang_2017_Eg_Eb}, the slope between
$(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ and $E_{g}$ is
$8\pi^{2}\varepsilon_{0} \mathrm{\AA}/(eN) \approx 0.436/N$, which
yields $N$ betweem 2 and 3, which is reasonable for the 2D materials
studied. We observe that materials with lower $E_{\mathrm{g}}$ ($<$4
eV) generally lie close to the regression line, while the deviation
becomes greater for materials with $E_{\mathrm{g}}>$4 eV, which has
also been observed in the $E_{\mathrm{b}}-E_{\mathrm{g}}$ relation of
2D materials \cite{Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}. We also
discover that the linearity between
$(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ and $E_{\mathrm{g}}$ is
better when the bandgap is calculated using the HSE06 hybrid
functionals, compared with that from the Perdew--Burk--Ernzerhof (PBE)
exchange correlations (details see Supplementary Section S2 and
Supplementary Figure S5), which can be explained by the fact that the
electronic structure, in particular the bandgap, is generally better
predicted at HSE06 level than PBE level \cite{Heyd_2005}. It should be
noted that although even more accurate estimation of both
$\varepsilon$ and $E_{\mathrm{g}}$ can be achieved via many-body
Green’s function method (GW) together with the Bethe-Salpeter
equation (BSE), the convergence of such method is known to be highly
affected by the dielectric screening of 2D materials
\cite{Hueser_2013_2Dvs3D}. Combining the accuracy, computational
effort and convergence, the choice of the HSE06 hybrid functional may
be most suitable to present the true 2D Moss-like relationship between
$\alpha^{\parallel}$ and $E_{\mathrm{g}}$.

We further examine the relation between $\alpha^{\perp}$ and the
thickness of a 2D material proposed in Eq. \ref{eq:2D-Moss-perp}. Here
we choose the thickness of as 2D material as its ``covalent''
thickness $\delta_{\mathrm{cov}}$, which is
defined as the longest distance along the z-direction between any two
atom nuclei plus their covalent radii:
\begin{equation}
  \label{eq:cov-thick}
  \delta_{\mathrm{cov}} = \mathrm{max}(|z^{i} - z^{j}|
  + r^{i}_{\mathrm{cov}} + r^{j}_{\mathrm{cov}})
\end{equation}
where i, j are two atoms in the 2D material and $r_{\mathrm{cov}}^{i}$
is the covalent radius of atom i (Figure \ref{fig-3}c). As shown in
Figure \ref{fig-3}b, $\alpha^{\perp}/(4 \pi \varepsilon_{0})$ indeed
shows an excellent linear correlation with $\delta_{\mathrm{cov}}$,
with $R^{2}=0.98$, and the slope very close to $1/4\pi$. In addition
to our theoretical predictions discussed above, the perfect linear
correlation between $\alpha^{\perp}$ and $\delta_{\mathrm{cov}}$ has
its strong physical meaning. Similar to the molecular polarizability
which characterizes the volume of electron cloud of an isolated
molecule \cite{Israelachvili_2011}, the 2D polarizability also
characterizes the volume of the electron cloud of a 2D material per
unit area (from its definition), and naturally represents the
thickness of the electron cloud of the 2D material. The fact that the
thickness of the electron cloud of a 2D material can be approximated
by the extension of valence states in the z-direction, explains the
close match between the linear slope in Figure \ref{fig-3}c and
$1/4\pi$. In other words, the universal scaling relation for
$\alpha^{\perp}$ indicates the quantity
$\alpha^{\perp}/\varepsilon_{0}$, is the dielectric characteristic
thickness of a 2D material. We propose that the experimental
measurment of the electronic polarizability
\cite{Antoine_1999,Cherniavskaya_2003,Krauss_1999_EFM}, can also be
extended to measure $\alpha^{\perp}$ of a 2D material, as a direct
estimation of it thickness, in comparison with the optical
ellipsometry techniques \cite{Weber_2010} widely used to estimate the
thickness of 2D materials, which requires empirical optical model and
parameter fitting.

To rule out the possibility that our conclusion is limited by the
number of materials used, we further validate our proposed 2D
Moss-like relations on the recently-published C2DB database
\cite{Haastrup_2018}, from which we extracted the dielectric
properties of over 230 2D materials calculated at the PBE level, and
overlap them with our results in Figure \ref{fig-3}b and \ref{fig-3}c
(further details see Supplementary Section S3). Althought the
dielectric properties may be overestimated at PBE level due to
underestimation of the bandgap compared with the more accurate HSE06
functionals, apparent linear trends can be observed for both
$\alpha^{\parallel}$ and $\alpha^{\perp}$, with the linear coefficient
very close to the HSE06 results. Therefore, the proposed universal 2D
Moss-like relations are confirmed.  We have also tested the potential
relation between the 2D polarizabilities with other physical
quantities, including the effective carrier mass, quantum capacitance
and total atomic polarizabilities, while no apparent correlations are
found (details see Supplementary Section S3).

In short, we have revealed the 2D analog of the Moss relation for both
polarization direction by using the 2D polarizability:
$\alpha^{\parallel}$ is inversely proportional to the minimal bandgap
$E_{\mathrm{g}}$, while $\alpha^{\perp}$ is the characteristic
thickness of the 2D material. Although their apparent forms in
Eq. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} seem different, we
will show the 2D Moss-like relations stem from the same origin. In
merit of the unit analysis, $\alpha^{\parallel}$ and $\alpha^{\perp}$
both have unit of $4\pi\varepsilon_{0} \cdot$[Length]. Specifically,
$\alpha^{\parallel}$ and $\alpha^{\perp}$ corresponds to
characteristic lengthes in- and out-of-plane, respectively. The
in-plane screened electrostatic potential $V(r)$ from a point charge
in an 2D plane, as a function of distance $r$:
$V(r) = {\displaystyle \frac{e}{4 \alpha^{\parallel}}}
\left[H_{0}({\displaystyle \frac{2\varepsilon_{0}
      r}{\alpha^{\parallel}}}) - Y_{0}( {\displaystyle \frac{2
      \varepsilon_{0}r}{\alpha^{\parallel}}})\right]$
\cite{Keldysh_1979_eps_multi,Pulci_2014}, where $H_{0}$ is the Struve
function and $Y_{0}$ is the Bessel function of second kind, is
assciated with the in-plane screening radius
$r_{0}^{\parallel}=\alpha^{\parallel}/(2 \varepsilon_{0})$, such that
$V(r,r/r^{\parallel}_{0} \gg 1)$ reduces to the simple Coulombic
potential in vacuum. Combining with the result that the thickness of
2D material is characterized by $\alpha^{\perp}/\varepsilon_{0}$, we
have drawn a generalized picture of the dielectric nature of 2D
materials via the 2D polarizability: the dielectric screening of a
point charge sitting in the middle of a 2D material can be viewed as
an ellipsoid with the length of principle axes to be
$\alpha^{\parallel}/(2 \varepsilon_{0})$ and
$\alpha^{\perp}/(2 \varepsilon_{0})$, respectively, analog to the
polarizability ellipsoid picture of molecules used in spectroscopy
\cite{Banwell_1994} (see Supplementary Figure S12). The in-plane
screening length is generally larger for a smaller bandgap
semiconductor, which qualitatively explains the inverse propotional
relation between $\alpha^{\parallel}$ and $E_{\mathrm{g}}$, a 2D
version of the Moss-relation.

@@

Apart from the universal Moss-like relations we propose for the
dielectric nature of 2D materials, it is also of high theoretical
interest to model the 2D-3D transition of dielectric properties. In
other words, can we describe the dielectric constants
$\varepsilon^{\parallel}_{\mathrm{Bulk}}$ and
$\varepsilon^{\perp}_{\mathrm{Bulk}}$ of a bulk layered material from
$\alpha^{\parallel}$ and $\alpha^{\perp}$ of the monolayer (see Figure
\ref{fig-4}a)? First, we see that the 2D polarizabilities for
individual layers in the bulk materials
$\alpha_{\mathrm{Bulk}}^{\parallel}$ and
$\alpha_{\mathrm{Bulk}}^{\perp}$, can be calculated using
Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def}, when $L$
becomes the bulk interlayer distance $L_{\mathrm{Bulk}}$. The
dielectric constants of the bulk material are then expressed as:
\begin{subequations}
\begin{eqnarray}
  \label{eq:3D-para}
  &\varepsilon^{\parallel}_{\mathrm{Bulk}} &= 1 + {\displaystyle \frac{\alpha_{\mathrm{bulk}}^{\parallel}}{\varepsilon_{0} L_{\mathrm{Bulk}}}}\\
  \label{eq:3D-perp}
  &\varepsilon^{\perp}_{\mathrm{Bulk}} &= \left(1 - \frac{\alpha_{\mathrm{Bulk}}^{\perp}}{\varepsilon_{0} L_{\mathrm{Bulk}}}\right)^{-1}
\end{eqnarray}
\end{subequations}
Note that $\alpha_{\mathrm{Bulk}}^{\parallel}$ and
$\alpha_{\mathrm{Bulk}}^{\perp}$ may not essentially be the same as
$\alpha$ of isolated layer, but still quite close as seen in Figure
\ref{fig-3}b and \ref{fig-3}c. Nevertheless we will first see how good
we can predict $\varepsilon_{\mathrm{Bulk}}^{\parallel}$ and
$\varepsilon_{\mathrm{Bulk}}^{\perp}$, when assuming
$\alpha_{\mathrm{bulk}}=\alpha$. We compare
$\varepsilon_{\mathrm{bulk}}^{\parallel}$ and
$\varepsilon_{\mathrm{bulk}}^{\perp}$ from first principles DFT
calculations compared with the values predicted using Eqs
\ref{eq:3D-para} and \ref{eq:3D-perp}, as show in Figure \ref{fig-4}b
and \ref{fig-4}c, respectively. Data calculated at both HSE06 and PBE
levels which give almost identical trends, indicating the generality
of such approach. Note although the stacking order is not considered
in Eqs. \ref{eq:3D-para} and \ref{eq:3D-perp}, we found that the
influence of stacking is minor (see Supplementary Figure SXX
\todo{Wait for Declan's data}). We observe that the majority of
predicted $\varepsilon_{\mathrm{bulk}}^{\parallel}$ values align along
the line $y=x$ , with a linear regression slope of 1.01 and $R^2$ of
0.97, indicating that such method indeed captures the transition from
$\alpha^{\parallel}$ to $\varepsilon_{\mathrm{Bulk}}^{\parallel}$. On
the other hand, we observe the predicted values of
$\varepsilon_{\mathrm{bulk}}^{\perp}$ has good agreement with the DFT
values when $E_{\mathrm{g}}>4$ eV, while the deviation becomes larger
when $E_{\mathrm{g}}$ reduces. The difference for the prediction of
$\varepsilon^{\parallel}$ and $\varepsilon^{\perp}$ means that
$\alpha^{\parallel}_{\mathrm{Bulk}}$ can generally be estimated from
its 2D counterpart, while $\alpha^{\perp}_{\mathrm{Bulk}}$ differs due
to interlayout coupling and overlap between induced dipoles, as also
observed in Figure \ref{fig-3}b, \ref{fig-3}c, and other studies
\cite{Andersen_2015_dielec_vdWH,Laturia_2018}. With a better model
describing $\alpha_{\mathrm{bulk}}^{\perp}$ as function of
$\alpha^{\perp}$ and the degree of interlayer coupling $\eta$
\cite{Tkatchenko_2012}, the dielectric transition from 2D to 3D would
be smoothly described.

As described in the previous section, the 2D Moss-like relation
between $\alpha^{\parallel}$ and $E_{g}$ is similar to the 3D Moss
relation between $\varepsilon$ and $E_{g}$, with a different power
law. Such difference in the power law can indeed be explained by
modern theory of dielectric properties.  Extend the approach
Eq. \ref{eq:alpha_perp_RPA} to the bulk material, and use the Bloch
presentation for wavefunctions in all dimensions, we derive (detailed
procedure see Supplementary Section S4):
\begin{equation}
  \label{eq:alpha-Eg-3D}
  \begin{aligned}[t]
  \varepsilon_{\mathrm{bulk}} &= 1 + \frac{2e^{2}}{\varepsilon_{0}(2\pi)^{3}}\int d^{3}\mathbf{k}
  \frac{|<u_{\mathrm{v}}(\mathbf{k})|\nabla|u_{\mathrm{v}}(k)>|^{2}}
  {E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})} \\
  &\propto E_{g}^{-\frac{1}{2}},\ \mathrm{when}\ \varepsilon_{\mathrm{Bulk}} \gg 1
\end{aligned}
\end{equation}
which recovers the 3D Moss relation. Therefore, the universal
$\alpha^{\parallel}-E_{\mathrm{g}}$ relation is indeed the Moss relation
in 2D world, while the power law of $E_{\mathrm{g}}$ and independence
of effective mass is a result of the confinement perpendicular to the
2D plane.

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{./img/fig4.pdf}
\caption{\label{fig-4} \textbf{Transition of dielectric properties
    from 2D to 3D systems}. \textbf{a}. Scheme for the 2D-3D
  transition. $\alpha$ in the 2D material is essentially equivalent to
  $\varepsilon$ in its bulk counterpart. \textbf{b}
  $\varepsilon_{\mathrm{bulk}}^{\parallel}$ calculated from DFT
  (y-axis) compared with the predicted value from 2D
  $\alpha^{\parallel}$ (x-axis), showing good correlation. \textbf{c}
  $\varepsilon_{\mathrm{bulk}}^{\perp}$ calculated from DFT (y-axis)
  compared with the predicted value from 2D $\alpha^{\parallel}$
  (x-axis). The predicted value is in good aggreement with the DFT
  calculation when $E_{\mathrm{g}}>4$ eV, due to minimal interlayer
  coupling. The comparisons in \textbf{b} and \textbf{c} are made
  based on both HSE06 (circles) and PBE (squares) levels.}
\end{figure}

>>>>

Figure \ref{fig-3}a shows the calculated bandgap $E_{\mathrm{g}}$
(blue dots) and polarizabilities (bar plots) of all the 2D materials
investigated, covering a wide spectrum range from far infrared to
ultraviolet. Note from dimension analysis, it is more intuitive to
express the polarizability as $\alpha/(4 \pi \varepsilon_{0})$, which
has unit of \AA. We find that $\alpha^{\parallel}$ has a general
descending trend when $E_{\mathrm{g}}$ increases. On the other hand,
no apparent trend between $\alpha^{\perp}$ and $E_{\mathrm{g}}$ is
observed (see Supplementary Section S2.2), which appears to be in good
agreement with our polarizability-based theoretical model. We now
validate Eq. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} using the
polarizabilities calculated by first principle calculations. Figure
\ref{fig-3}b shows $(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ (in
\AA{}) as a function of $E_{\mathrm{g}}$ (in eV) for the 2D materials
investiaged (circle dots), with a linear regression slope of ~0.182
and $R^{2}$ of 0.84. From Ref. \citenum{Jiang_2017_Eg_Eb}, the slope
between $(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ and $E_{g}$ is
$8\pi^{2}\varepsilon_{0} \mathrm{\AA}/(eN) \approx 0.436/N$, which
yields $N$ betweem 2 and 3, which is reasonable for the 2D materials
studied. We observe that materials with lower $E_{\mathrm{g}}$ ($<$4
eV) generally lie close to the regression line, while the deviation
becomes greater for materials with $E_{\mathrm{g}}>$4 eV, which has
also been observed in the $E_{\mathrm{b}}-E_{\mathrm{g}}$ relation of
2D materials \cite{Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}. We also
discover that the linearity between
$(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ and $E_{\mathrm{g}}$ is
better when the bandgap is calculated using the HSE06 hybrid
functionals, compared with that from the Perdew--Burk--Ernzerhof (PBE)
exchange correlations (details see Supplementary Section S2 and
Supplementary Figure S5), which can be explained by the fact that the
electronic structure, in particular the bandgap, is generally better
predicted at HSE06 level than PBE level \cite{Heyd_2005}. It should be
noted that although even more accurate estimation of both
$\varepsilon$ and $E_{\mathrm{g}}$ can be achieved via many-body
Green’s function method (GW) together with the Bethe-Salpeter equation
(BSE), the convergence of such method is known to be highly affected
by the dielectric screening of 2D materials
\cite{Hueser_2013_2Dvs3D}. Combining the accuracy, computational
effort and convergence, the choice of the HSE06 hybrid functional may
be most suitable to present the true 2D Moss-like relationship between
$\alpha^{\parallel}$ and $E_{\mathrm{g}}$.

We further examine the relation between $\alpha^{\perp}$ and the
thickness of a 2D material proposed in
Eq. \ref{eq:2D-Moss-perp}. Here we choose the ``covalent'' thickness
$\delta_{\mathrm{cov}}$ of a 2D material, which is defined as the
longest distance along the z-direction between any two atom nuclei
plus their covalent radii:
\begin{equation}
  \label{eq:cov-thick}
  \delta_{\mathrm{cov}} = \mathrm{max}(|z^{i} - z^{j}|
  + r^{i}_{\mathrm{cov}} + r^{j}_{\mathrm{cov}})
\end{equation}
where i, j are two atoms in the 2D material and $r_{\mathrm{cov}}^{i}$
is the covalent radius of atom i (Figure \ref{fig-3}c inset). As shown
in Figure \ref{fig-3}c, $\alpha^{\perp}/(4 \pi \varepsilon_{0})$
indeed shows an excellent linear correlation with
$\delta_{\mathrm{cov}}$, with $R^{2}=0.98$, and the slope very close
to $1/4\pi$. In addition to our theoretical predictions discussed
above, the perfect linear correlation between $\alpha^{\perp}$ and
$\delta_{\mathrm{cov}}$ has its strong physical meaning. Similar to
the molecular polarizability which characterizes the volume of
electron cloud of an isolated molecule \cite{Israelachvili_2011}, the
2D polarizability also characterizes the volume of the electron cloud
per unit area (from its definition), and naturally represents the
thickness of the electron cloud of the 2D material. The fact that the
thickness of the electron cloud can be approximated by the extension
of valence states in the z-direction, explains the close match between
the linear slope in Figure \ref{fig-3}c and $1/4\pi$ (see
Supplementary Section S4.1). In other words, the universal scaling
relation for $\alpha^{\perp}$ indicates the quantity
$\alpha^{\perp}/\varepsilon_{0}$, is the dielectric characteristic
thickness of a 2D material. We propose that the experimental
measurment of the electronic polarizability
\cite{Antoine_1999,Cherniavskaya_2003,Krauss_1999_EFM}, can also be
extended to measure $\alpha^{\perp}$ of a 2D material, as a direct
estimation of it thickness, in comparison with the optical
ellipsometry techniques \cite{Weber_2010} widely used to estimate the
thickness of 2D materials, which requires empirical optical model and
parameter fitting.

The universal relations of 2D polarizabilities are not
coincidence. Combining recent theoretical findings of the linear
relation between exciton binding energy $E_{\mathrm{b}}$ and
$E_{\mathrm{g}}$ of 2D materials
\cite{Choi_linear_2015,Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}, and the
fact that the $E_{\mathrm{b}}$ is roughly inversely proportional to
$\alpha^{\parallel}$ \cite{Pulci_2014}, it is reasonable to have a
general Moss-like relation between $E_{\mathrm{g}}$ and
$1/\alpha^{\parallel}$. Moreover, the bandgap-independent relation of
2D $\alpha^{\perp}$ resembles molecular polarizabilities of conjugate
molecules \cite{Davies_1952}, fullerenes \cite{Sabirov_2014} and
carbon nanotubes \cite{Benedict_1995}, which are also shown to be
geometry-dependent. To rule out the possibility that our conclusion is
limited by the number of materials used, we further validate our
proposed 2D Moss-like relations on the recently-published C2DB
database \cite{Haastrup_2018}, from which we extracted the dielectric
properties of over 230 2D materials calculated at the PBE level, and
overlap them with our results in Figure \ref{fig-3}b and \ref{fig-3}c
(further details see Supplementary Section S3). Althought the
dielectric properties may be overestimated at PBE level due to
underestimation of the bandgap compared with the more accurate HSE06
functionals, apparent linear trends can be observed for both
$\alpha^{\parallel}$ and $\alpha^{\perp}$, with the linear coefficient
very close to the HSE06 results. Therefore, the proposed universal 2D
Moss-like relations are confirmed.  We have also tested the potential
relation between the 2D polarizabilities with other physical
quantities, including the effective carrier mass, quantum capacitance
and total atomic polarizabilities, while no apparent correlations are
found (details see Supplementary Section S3).

In short, we have revealed the 2D analog of the Moss relation by both
theoretical modeling and first principles calculations:
$\alpha^{\parallel}$ is inversely proportional to the minimal bandgap
$E_{\mathrm{g}}$, while $\alpha^{\perp}$ is the characteristic
thickness of the 2D material. Although their apparent forms in
Eq. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} seem different, we
will show the 2D Moss-like relations stem from the same origin. In
merit of the unit analysis, $\alpha^{\parallel}$ and $\alpha^{\perp}$
both have unit of $4\pi\varepsilon_{0} \cdot$[Length]. Specifically,
$\alpha^{\parallel}$ and $\alpha^{\perp}$ corresponds to
characteristic lengthes in- and out-of-plane, respectively. The
in-plane screened electrostatic potential $V(r)$ from a point charge
in an 2D plane, as a function of distance $r$:
$V(r) = {\displaystyle \frac{e}{4 \alpha^{\parallel}}}
\left[H_{0}({\displaystyle \frac{2\varepsilon_{0}
      r}{\alpha^{\parallel}}}) - Y_{0}( {\displaystyle \frac{2
      \varepsilon_{0}r}{\alpha^{\parallel}}})\right]$
\cite{Keldysh_1979_eps_multi,Pulci_2014}, where $H_{0}$ is the Struve
function and $Y_{0}$ is the Bessel function of second kind, is
assciated with the in-plane screening radius
$r_{0}^{\parallel}=\alpha^{\parallel}/(2 \varepsilon_{0})$, such that
$V(r,r/r^{\parallel}_{0} \gg 1)$ reduces to the simple Coulombic
potential in vacuum. Combining with the result that the thickness of
2D material is characterized by $\alpha^{\perp}/\varepsilon_{0}$, we
have drawn a generalized picture of the dielectric nature of 2D
materials via the 2D polarizability: the dielectric screening of a
point charge sitting in the middle of a 2D material can be viewed as
an ellipsoid with the length of principle axes to be
$\alpha^{\parallel}/(2 \varepsilon_{0})$ and
$\alpha^{\perp}/(2 \varepsilon_{0})$, respectively, analog to the
polarizability ellipsoid picture of molecules used in spectroscopy
\cite{Banwell_1994} (see Supplementary Figure S12). The in-plane
screening length is generally larger for a smaller bandgap
semiconductor, which qualitatively explains the inverse propotional
relation between $\alpha^{\parallel}$ and $E_{\mathrm{g}}$, a 2D
version of the Moss-relation.

@@

Apart from the universal Moss-like relations we propose for the
dielectric nature of 2D materials, it is also of high theoretical
interest to model the 2D-3D transition of dielectric properties. In
other words, can we describe the dielectric constants
$\varepsilon^{\parallel}_{\mathrm{Bulk}}$ and
$\varepsilon^{\perp}_{\mathrm{Bulk}}$ of a bulk layered material from
$\alpha^{\parallel}$ and $\alpha^{\perp}$ of the monolayer (see Figure
\ref{fig-4}a)? First, we see that the 2D polarizabilities for
individual layers in the bulk materials
$\alpha_{\mathrm{Bulk}}^{\parallel}$ and
$\alpha_{\mathrm{Bulk}}^{\perp}$, can be calculated using
Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def}, when $L$
becomes the bulk interlayer distance $L_{\mathrm{Bulk}}$. The
dielectric constants of the bulk material are then expressed as:
\begin{subequations}
\begin{eqnarray}
  \label{eq:3D-para}
  &\varepsilon^{\parallel}_{\mathrm{Bulk}} &= 1 + {\displaystyle \frac{\alpha_{\mathrm{bulk}}^{\parallel}}{\varepsilon_{0} L_{\mathrm{Bulk}}}}\\
  \label{eq:3D-perp}
  &\varepsilon^{\perp}_{\mathrm{Bulk}} &= \left(1 - \frac{\alpha_{\mathrm{Bulk}}^{\perp}}{\varepsilon_{0} L_{\mathrm{Bulk}}}\right)^{-1}
\end{eqnarray}
\end{subequations}
Note that $\alpha_{\mathrm{Bulk}}^{\parallel}$ and
$\alpha_{\mathrm{Bulk}}^{\perp}$ may not essentially be the same as
$\alpha$ of isolated layer, but still quite close as seen in Figure
\ref{fig-3}b and \ref{fig-3}c. Nevertheless we will first see how good
we can predict $\varepsilon_{\mathrm{Bulk}}^{\parallel}$ and
$\varepsilon_{\mathrm{Bulk}}^{\perp}$, when assuming
$\alpha_{\mathrm{bulk}}=\alpha$. We compare
$\varepsilon_{\mathrm{bulk}}^{\parallel}$ and
$\varepsilon_{\mathrm{bulk}}^{\perp}$ from first principles DFT
calculations compared with the values predicted using Eqs
\ref{eq:3D-para} and \ref{eq:3D-perp}, as show in Figure \ref{fig-4}b
and \ref{fig-4}c, respectively. Data calculated at both HSE06 and PBE
levels which give almost identical trends, indicating the generality
of such approach. Note although the stacking order is not considered
in Eqs. \ref{eq:3D-para} and \ref{eq:3D-perp}, we found that the
influence of stacking is minor (see Supplementary Figure SXX
\todo{Wait for Declan's data}). We observe that the majority of
predicted $\varepsilon_{\mathrm{bulk}}^{\parallel}$ values align along
the line $y=x$ , with a linear regression slope of 1.01 and $R^2$ of
0.97, indicating that such method indeed captures the transition from
$\alpha^{\parallel}$ to $\varepsilon_{\mathrm{Bulk}}^{\parallel}$. On
the other hand, we observe the predicted values of
$\varepsilon_{\mathrm{bulk}}^{\perp}$ has good agreement with the DFT
values when $E_{\mathrm{g}}>4$ eV, while the deviation becomes larger
when $E_{\mathrm{g}}$ reduces. The difference for the prediction of
$\varepsilon^{\parallel}$ and $\varepsilon^{\perp}$ means that
$\alpha^{\parallel}_{\mathrm{Bulk}}$ can generally be estimated from
its 2D counterpart, while $\alpha^{\perp}_{\mathrm{Bulk}}$ differs due
to interlayout coupling and overlap between induced dipoles, as also
observed in Figure \ref{fig-3}b, \ref{fig-3}c, and other studies
\cite{Andersen_2015_dielec_vdWH,Laturia_2018}. With a better model
describing $\alpha_{\mathrm{bulk}}^{\perp}$ as function of
$\alpha^{\perp}$ and the degree of interlayer coupling \cite{Tkatchenko_2012}, the dielectric transition from 2D to 3D would
be smoothly described.

Although we have extensively shown that the treatment for the
dielectric nature differs in 2D (polarizability) and 3D (dielectric
constant) scenarios, a general picture of the dielectric properties in
both dimensions can still be drawn by studying the dielectric
anisotropy. The dielectric anisotropy index $\eta$ is defined as:
\begin{equation}
  \label{eq:anisotropy}
  \begin{aligned}[t]
    \eta =
    \begin{cases}
      {\displaystyle \min_{i \neq j}}
      {\displaystyle
        \left(\frac{\varepsilon^{ii}}{\varepsilon^{jj}}\right)},
      \ \mathrm{Bulk\ Materials}\\
      {\displaystyle \min_{i \neq j}}
      {\displaystyle
        \left(\frac{\alpha^{ii}}{\alpha^{jj}}\right)},
      \ \mathrm{2D\ Materials}\\
    \end{cases}
  \end{aligned}
\end{equation}
$\eta=1$ indicates the material has isotropic dielectric properties
while $\eta \to 0$ means the dielectric property is highly
anisotropic. Figure XX \todo{TBD} shows the phase diagram of $\eta$ as
function of $E_{\mathrm{g}}$ for 2D materials and their bulk
counterparts. Interestingly, the 2D materials (\todo{marker shape})
can be clearly distinguished from the layered bulk materials
(\todo{marker shape}). The boundary separating the 2D and layered bulk
materials is determined using an least-square support vector machine
(LS-SVM) classification algorithm, and can be linearly approximated by
the equation \todo{TBD}. The much lower $\eta$ values of 2D materials
compared with their bulk counterparts indicates a high dielectric
anisotropy, which is responsible for the unique 2D optoelectronic
properties, such as electrostatic transparency
\cite{Liluhua_2014,Tian_2016,Li_2018} and large exciton binding energy
\cite{Pulci_2014,Tran_2014,Chernikov_2014_EB_MoS2_2D3D,Berkelbach_2013}. We
also observe that $\eta$ of 2D materials increase almost linearly with
$E_{\mathrm{g}}$, while such trend is absent for layered bulk
materials. The observations above can be explained by the principles
presented in thie work. As a result from the limited layer thickness
(mostly 3--10 \AA{}), $\alpha^{\perp}$ of a monolayer 2D material
varies much less than $\alpha^{\parallel}$ (Figure \ref{fig-3}b and
\ref{fig-3}c), which explains the domination of $E_{\mathrm{g}}$ in
$\eta$ of 2D materials. On the other hand, the fact that
$\varepsilon^{\perp}_{\mathrm{Bulk}}$ is generally larger than the
values calculated from $\alpha^{\perp}$ of monolayer due to interlayer
coupling (Figure \ref{fig-4}c), gives rise to larger $\eta$ for
layered bulk materials compared with the corresponding monolayer, and
making it possible to separate the 2D and layered bulk materials from
the $\eta-E_{\mathrm{g}}$ phase diagram.

\todo[inline]{I have some doubt how to handle the next paragraph, keep the status quo}
As described in the previous section, the 2D Moss-like relation
between $\alpha^{\parallel}$ and $E_{g}$ is similar to the 3D Moss
relation between $\varepsilon$ and $E_{g}$, with a different power
law. Such difference in the power law can indeed be explained by
modern theory of dielectric properties.  Extend the approach
Eq. \ref{eq:alpha_perp_RPA} to the bulk material, and use the Bloch
presentation for wavefunctions in all dimensions, we derive (detailed
procedure see Supplementary Section S4):
\begin{equation}
  \label{eq:alpha-Eg-3D}
  \begin{aligned}[t]
  \varepsilon_{\mathrm{bulk}} &= 1 + \frac{2e^{2}}{\varepsilon_{0}(2\pi)^{3}}\int d^{3}\mathbf{k}
  \frac{|<u_{\mathrm{v}}(\mathbf{k})|\nabla|u_{\mathrm{v}}(k)>|^{2}}
  {E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})} \\
  &\propto E_{g}^{-\frac{1}{2}},\ \mathrm{when}\ \varepsilon_{\mathrm{Bulk}} \gg 1
\end{aligned}
\end{equation}
which recovers the 3D Moss relation. Therefore, the universal
$\alpha^{\parallel}-E_{\mathrm{g}}$ relation is indeed the Moss
relation in 2D world, while the power law of $E_{\mathrm{g}}$ and
independence of effective mass is a result of the confinement
perpendicular to the 2D plane.

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.85\linewidth]{./img/fig4.pdf}
\caption{\label{fig-4} \textbf{Transition of dielectric properties
    from 2D to 3D systems}. \textbf{a}. Scheme for the 2D-3D
  transition. $\alpha$ in the 2D material is essentially equivalent to
  $\varepsilon$ in its bulk counterpart. \textbf{b}
  $\varepsilon_{\mathrm{bulk}}^{\parallel}$ calculated from DFT
  (y-axis) compared with the predicted value from 2D
  $\alpha^{\parallel}$ (x-axis), showing good correlation. \textbf{c}
  $\varepsilon_{\mathrm{bulk}}^{\perp}$ calculated from DFT (y-axis)
  compared with the predicted value from 2D $\alpha^{\parallel}$
  (x-axis). The predicted value is in good aggreement with the DFT
  calculation when $E_{\mathrm{g}}>4$ eV, due to minimal interlayer
  coupling. The comparisons in \textbf{b} and \textbf{c} are made
  based on both HSE06 (circles) and PBE (squares) levels.}
\end{figure}
